---
title: "Intro to Probability & Statistics"
subtitle: "DSCI 501 - Winter 2022"  
author: "Layla Bouzoubaa"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#07294D",
  secondary_color = "#FFC600",
  inverse_header_color = "#FFFFFF"
)
```

## Objectives:

- Understand the principle of counting  
- Learn how to find permutations  
- Learn how to calculate combinations
- Know how to compute independent probability  
- Know how to compute conditional probability 
- Understand the different types of variables  
- Understand Bayes rule and how it can be useful 
- Know the different types of variables  
- Understand what expectation is  
- Understand the importance of variance & standard variation  
- Know the main types of distributions  
- Understand the Central Limit Theorem  
- Know how to calculate a confidence interval  
- Know how to perform a hypothesis test
- Understand the significance of a p-value  

---
class: inverse center middle

## Counting

---

## Counting


---
## Permutations

---
## Combinations

---
class: inverse center middle

## Probability

---
class: inverse center middle

## Statistical Foundations


---

## Variables

---

## Expectation

> This is a blockquote following a header.
>
> When something is important enough, you do it even if the odds are not in your favor.

---

## Variance

#### R Code

```{r eval=FALSE}
ggplot(gapminder) +
  aes(x = gdpPercap, y = lifeExp, size = pop, color = country) +
  geom_point() +
  facet_wrap(~year)
```

---

## Standard Deviation

```{r eval=FALSE}
dplyr::starwars %>% dplyr::slice_sample(n = 4)
```

---

## Distributions

```{r message=TRUE, eval=requireNamespace("cli", quietly = TRUE)}
cli::cli_alert_success("It worked!")
```

```{r message=TRUE}
message("Just a friendly message")
```

```{r warning=TRUE}
warning("This could be bad...")
```


```{r error=TRUE}
stop("I hope you're sitting down for this")
```


---
layout: true

## Central Limit Theorem

---
exclude: `r if (requireNamespace("tibble", quietly=TRUE)) "false" else "true"`

```{r eval=requireNamespace("tibble", quietly=TRUE)}
tibble::as_tibble(mtcars)
```

---

## Confidence Intervals

```{r}
knitr::kable(head(mtcars), format = 'html')
```

---

## Hypthesis Testing

```{r eval=requireNamespace("DT", quietly=TRUE)}
DT::datatable(head(mtcars), fillContainer = FALSE, options = list(pageLength = 4))
```

